---
title: "Lab 00 - Hello IDS!"
author: "Andrew Morris"
date: "20/09/2024"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Andrew", "Adam", "Helen", 
           "Max", "Sarah", "Liv"),
  github_username = c("pukklemaster", "helenrmiller", "adamlaycock", 
                      "MaxwellPohlman", "Sarahstewart142", "oliviaharris1"), 
  colour = c("mediumaquamarine", "thistle1", "forestgreen", 
             "slategray3", "powderblue", "violetred"),
  hobby = c("Knitting", "Crochet", "Guitar", 
            "Climbing", "Swimming", "Netball"),
  favourite_number = c(7, 4, 7, 10, 6, 4)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The bar chart shows each of the group members usernames on the x axis and their favourite number on the y axis, shown through a bar chart.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "User Names", 
          y = "Favourite Number",
          title = "Group members favourite numbers")
```

The axis labels have been changed on the x and y axis and also on the title of the graph

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

the bar plot is plotting the hobbys on the x axis and how many people have chose that hobby on the y axis
